---
title: "analysis"
output: html_document
editor_options: 
  chunk_output_type: inline
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#libraries & loading
```{r}

a <- read.csv("Experiment_2.csv")
# Preprocess data
a$UniqueID=factor(paste(a$Experiment, a$Participant.Number))
a$Previous.Rounds=a$Round-1
np=subset(a, Punishment.Round=="N")
#set working directory

library(tidyverse) ; library(ggplot2) ; library(patchwork)

#sam <- jags_output #load previously created jags object
#map <- read.csv("MAP.13.csv") #load previously created MAP values
df0 <- read.csv("MAP13_df_0.csv") #the one with vals 0-20
df <- df0
df2 <- read.csv("MAP13_df.csv") #load previously created MAP values + participant info


df_nb_con = df %>% subset(Condition == 0) #in no breakfast condition/group
df_b_con = df %>% subset(Condition == 1) #in breakfast condition/group

df_nb = df %>% subset(BreakfastToday == 0) #ACTUALLY no breakfast
df_b = df %>% subset(BreakfastToday == 1) #ACTUALLY breakfast
```

#PBETA (preference slope)
#lm models
```{r}
#  
model_pbeta = lm(pbeta ~ BreakfastToday + BreakfastUsually + HowHungry, df)
summary(model_pbeta)
report(model_pbeta)
```

# t-tests for PBETA
```{r} 
# Since data is not normally distributed we break assumptions, while performing the t test
qqnorm(df$pbeta)

# gender effects
test = t.test(df$pbeta[df$Gender=="F"],df$pbeta[df$Gender=="M"]) #p = .007
boxplot(df$pbeta[df$Gender=="F"],df$pbeta[df$Gender=="M"])
report(test)

#breakfast/no breakfast condition
test2 = t.test(df$pbeta[df$Condition==0],df$pbeta[df$Condition==1]) #p = .136
#ikke normalfordelt! (+ ceiling effect...)

boxplot(df$pbeta[df$Condition==0],df$pbeta[df$Condition==1])

report(test2)

test3 = t.test(df$pbeta[df$BreakfastToday==0],df$pbeta[df$BreakfastToday==1]) #p = .136
#ikke normalfordelt! (+ ceiling effect...)

boxplot(df$pbeta[df$Condition==0],df$pbeta[df$Condition==1])

report(test3)
```

#preference (pbeta) slopes
```{r}
mydat <- tibble(x=0:20, 
                y = 0:20)
# Plot all slopes
ggplot(mydat, aes(x=x, y=y)) + 
  geom_segment(df, mapping = aes(x = 0, xend = 20, y = 0, yend = pbeta*20, color = as.factor(BreakfastToday))) +
  xlim(0, 20) +
  ylim(0, 20) +
  xlab("Belief about others' contribution") +
  ylab("My contribution") +
  labs(color = "Condition") +
  ggtitle("Individual Slopes for Cooperative Preferences (color = condition)")

# Plot mean slopes
ggplot(mydat, aes(x=x, y=y)) + 
  geom_segment(df_nb, mapping = aes(x = 0, xend = 20, y = 0, yend = mean(pbeta*20), color = as.factor(BreakfastToday))) +
  geom_segment(df_b, mapping = aes(x = 0, xend = 20, y = 0, yend = mean(pbeta*20), color = as.factor(BreakfastToday))) +
  xlim(0, 20) +
  ylim(0, 20) +
  xlab("Belief about others' contribution") +
  ylab("My contribution") +
  labs(color = "Condition") +
  ggtitle("Mean group slopes for Cooperative Preferences (ACTUAL)")

# Plot mean slopes
ggplot(mydat, aes(x=x, y=y)) + 
  geom_segment(df_nb_con, mapping = aes(x = 0, xend = 20, y = 0, yend = mean(pbeta*20), color = as.factor(Condition))) +
  geom_segment(df_b_con, mapping = aes(x = 0, xend = 20, y = 0, yend = mean(pbeta*20), color = as.factor(Condition))) +
  xlim(0, 20) +
  ylim(0, 20) +
  xlab("Belief about others' contribution") +
  ylab("My contribution") +
  labs(color = "Condition") +
  ggtitle("Mean group slopes for Cooperative Preferences (CONDITION)") #+
  #geom_errorbar()

?polpsline
# Condition leaves a bigger difference in slopes. also against what we would think since condition is the no breakfast groups but also containing the people who accidently ate breakfast anyway
```

#LAMBDA (decay rate)
Lambda: Is one's decay rate determined by breakfast eating? 
In the paper they find the no breakfast group to be more influenced by the other group members 
aka weighting you belief over preference. Aka smaller decay rate
```{r}
#
model_lambda = lm(lambda ~ BreakfastToday + BreakfastUsually + HowHungry, df)

ggplot(df, aes(x=as.factor(BreakfastToday), y=lambda)) + 
  geom_boxplot() +
  geom_point() + 
  xlab("Condition") +
  ylab("Value") +
  ggtitle("Decay rate per condition")

```

#OMEGA1 (initial weighting of beliefs)
```{r}
#
model_omega1 = lm(omega1 ~ BreakfastToday + BreakfastUsually + HowHungry, df)
report(model_omega1)

ggplot(df, aes(x=as.factor(BreakfastToday), y=omega1)) + 
  geom_boxplot() +
  geom_point() +
  xlab("Condition") +
  ylab("Value") +
  ggtitle("Initial weighting of beliefs per condition")
```

#GAMMA
The higher the gamma, the more you weight your beliefs from last round
The lower, the more you weight what you observed in the last round
Hungry people should have lower gamma since they weight more about what they observed / influence (?)
```{r}
#
model_gamma = lm(gamma ~ BreakfastToday + BreakfastUsually + HowHungry, df)
report(model_gamma)

# Boxplot
ggplot(df, aes(x=as.factor(BreakfastToday), y=gamma)) + 
  geom_boxplot() +
  geom_point() +
  xlab("Condition") +
```



```{r}
ylab("Value") +
  ggtitle("Parameter weighting of beliefs per condition")
```

#Examples of data vs. slope
```{r}
#### Check one participant and compare lagged contribution with our pbeta
#
ID = df$UniqueID[6]
slope = df$pbeta[6]
data=subset(np, UniqueID == paste(ID))
data= subset(data, Punishment.Round=="N")

ggplot(data, aes(x=Lagged.MCO, y=Contribution)) + 
  geom_segment(mydat, mapping = aes(x = 0, xend = 20, y = 0, yend = mean(slope*20))) +
  geom_point() +
  xlim(0, 20) +
  ylim(0, 20) +
  xlab("Lagged contribution of others / Belief about others' contribution") +
  ylab("My contribution") +
  labs(color = "Condition") +
  ggtitle("Unique Participant ID:", paste(ID))

#
ID = df$UniqueID[43]
slope = df$pbeta[43]
data=subset(np, UniqueID == paste(ID))
data= subset(data, Punishment.Round=="N")

ggplot(data, aes(x=Lagged.MCO, y=Contribution)) + 
  geom_segment(mydat, mapping = aes(x = 0, xend = 20, y = 0, yend = mean(slope*20))) +
  geom_point() +
  xlim(0, 20) +
  ylim(0, 20) +
  xlab("Lagged contribution of others / Belief about others' contribution") +
  ylab("My contribution") +
  labs(color = "Condition") +
  ggtitle("Unique Participant ID:", paste(ID))

#
ID = df$UniqueID[262]
slope = df$pbeta[262]
data=subset(np, UniqueID == paste(ID))
data= subset(data, Punishment.Round=="N")

ggplot(data, aes(x=Lagged.MCO, y=Contribution)) + 
  geom_segment(mydat, mapping = aes(x = 0, xend = 20, y = 0, yend = mean(slope*20))) +
  geom_point() +
  xlim(0, 20) +
  ylim(0, 20) +
  xlab("Lagged contribution of others / Belief about others' contribution") +
  ylab("My contribution") +
  labs(color = "Condition") +
  ggtitle("Unique Participant ID:", paste(ID))

```

# The mean pbeta slopes for each condition plot
```{r}

# Make mean slopes + error 
# Make data for the slope
slope0 = mean(df$pbeta[df$Condition == 0])
slope0
slope1 = mean(df$pbeta[df$Condition == 1])
slope1

xs = seq(0, 20, by =1)
ys0 = slope0*xs
ys1 = slope1*xs
dat0 = data.frame(xs, ys0)
dat1 = data.frame(xs, ys1)
sd0 = sd(df$pbeta[df$Condition == 0])
sd0
sd1 = sd(df$pbeta[df$Condition == 1])
sd1

dat0$grp <- paste("No Breakfast")
dat1$grp <- paste("Breakfast")

plot1 = ggplot(dat1, mapping = aes(x = xs, y = ys1, color = "Breakfast")) + 
  geom_line() +
  xlim(-1, 20) +
  ylim(-1, 20) +
  xlab("Belief about others' contribution") +
  ylab("Contribution") +
  labs(color = "Condition") +
  ggtitle("Mean pbeta slope for each condition") + 
  #geom_errorbar(aes(ymin = ys-sd, ymax = ys+sd)) +
  geom_ribbon(aes(y = ys1, ymin = ys1 - sd1, ymax = ys1 + sd1, color = "+- one standard deviation",  fill = "skyblue"), show.legend = FALSE, alpha = .2) 

plot1 +  
  geom_line(dat0, mapping = aes(x = xs, y = ys0, color = "No Breakfast")) + 
  geom_ribbon(aes(y = ys0, ymin = ys0 - sd1, ymax = ys0 + sd0, color = "+- one standard deviation", fill = "red"), show.legend = FALSE, alpha = .2) +
  scale_color_manual(
      values = c(
           "No Breakfast"="red",
           "Breakfast"="blue",
            "+- one standard deviation" = "lightgrey"))

```

